VFTS682: a confirmed dynamical ejection?

### 2018-05-09 VFTS682.tex
minor stuff

To compare the astrometry of VFTS682 and derive its peculiar motion,
we then select data from the Gaia DR2 catalog for two regions: the
``surroundings'' of VFTS 682, and the ``R136 cluster''. The
surrounding region is defined by all the stars in a target of 10 arcminutes around
VFTS682 fulfilling the following criteria: we require \texttt{visibility\_period} >= 5,
\texttt{astrometric\_excess\_noise} <= 1, the error on the proper
motion components to be smaller than 0.1\,$\mathrm{mas\ yr^{-1}}$,
and the proper motion components themselves to be smaller than
2\,$\mathrm{mas\ yr^{-1}}$ in absolute value. At the distance to the
LMC, $1\mathrm{mas\ yr^{-1}}\simeq250\,\kms$ \citep[e.g.,][]{lennon:18}, so the cut on the values
of the proper motions removes stars that would have projected
tangential velocities in excess of $\sim$500\,$\kms$, which are most
likely to be foreground stars \todo{clean phrasing here}.
This selection yields 437 stars.

@@

\subsection{Is it a runaway star?}
We first address the question of whether VFTS682 is a typical star in
its surroundings from the kinematic point of view, or whether it is a
runaway star with a significantly large peculiar velocity. The former is what should
be expected if it formed where we observe it today, in relative
isolation from other massive stars. We calculate the velocity relative
to the general population in its surroundings, shown as blue dots in
the large panel of\Figref{fig:main}, assuming a distance of
$D=50$\,kpc.

>>>>

To compare the astrometry of VFTS682 and derive its peculiar motion,
we then select data from the Gaia DR2 catalog for two regions: the
``surroundings'' of VFTS 682, and the ``R136 cluster''. The
surrounding region is defined by all the stars in a target of 10 arcminutes around
VFTS682 fulfilling the following criteria: we require \texttt{visibility\_period} >= 5,
\texttt{astrometric\_excess\_noise} <= 1, the error on the proper
motion components to be smaller than 0.1\,$\mathrm{mas\ yr^{-1}}$,
and the proper motion components themselves to be smaller than
2\,$\mathrm{mas\ yr^{-1}}$ in absolute value. At the distance to the
LMC, $1\mathrm{mas\ yr^{-1}}\simeq250\,\kms$ \citep[e.g.,][]{lennon:18}, so the cut on the values
of the proper motions removes stars that would have projected
tangential velocities in excess of $\sim$500\,$\kms$, which are most
likely to be foreground stars.
This selection yields 437 stars.

@@

\subsection{Is it a runaway star?}
We first address the question of whether VFTS682 is a typical star in
its surroundings from the kinematic point of view, or whether it is a
runaway star with a significantly large peculiar velocity. The former is what should
be expected if it formed where we observe it today, in relative
isolation from other massive stars. We calculate the velocity relative
to the general population in its surroundings, shown as blue dots in
the large panel of \Figref{fig:main}, assuming a distance of
$D=50$\,kpc.
